Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-08-13 neurips-20/response/neurips_2020_author_response.tex
rebuttal

@@

\textbf{Examples:} We agree that earlier examples would be beneficial to help readers build intuition, and thank the reviewers for the suggestions. We plan to use abstain and variance estimation as running examples for different quadrants starting from Section 2.

\textbf{Motivation of dimension (particularly for continuous predictions):}  The surrogate loss is one small part of the entire learning algorithm, whose complexity is a function of the prediction dimension among other things.  While reducing prediction dimension from $n$ to $n-1$ may not be overwhelmingly beneficial, an exponential reduction, like that observed in the BEP abstain surrogate [22], can significantly improve the efficiency of the learning algorithm as a whole.  As demonstrated in this paper, prediction dimension bounds are often a function of the number of outcomes $n$, which does not bode well for infinite outcome tasks.  This highlights the beauty of variance having a \emph{constant} prediction dimension, though this does not generalize across continuous prediction problems.  Other continuous predictions problems such as upper confidence bounds are not well understood, despite its practical desirability for estimating numerical model reliability in engineering domains.

\textbf{R1:}  We hope the earlier introduction of examples will improve clarity and improve the intuition for notation. $\ker(W)$ is the kernel of the matrix $W$.
For broader impacts, we note that the conference organizers write, ``if your work is very theoretical or is general enough that there is no particular application foreseen, then you are free to write that a Broader Impact discussion is not applicable.’’\footnote{\url{https://neurips.cc/Conferences/2020/PaperInformation/NeurIPS-FAQ}}

\textbf{R2:}  Regarding indirection elicitation, the implication of inclusion is correct, and we will add this for intuition.

@@

\textbf{R5:} Regarding Theorems 2 and 3, it is correct that the best lower bound is the supremum over choices of $r$ and $p$. We agree that could be a good presentation, although stylistically we had reasons for our current approach. These include: this suprema does not seem to have a nice closed form; one’s intuition often leads to the best particular choice of $r$ and $p$; and this presentation matches that of [21, Theorem 16].

The relint(simplex) question is interesting. In every example we’ve seen, the supremum p is in the interior, but we cannot prove this will always be true; it’s an open question.

We agree Theorem 1 is rather straightforward (it is more of an observation than a result, per se).  We felt it important to emphasize given how crucial it is for proving Theorems 2 and 3.

Regarding the citation in line 161, more general proofs have been derived by [28] (multiclass classification) and [21] (general matrix losses), but the proof is given most rigorously by [2].  We will add the other citations. Thanks for the clarification on [28] and its NeurIPS 2012 version.

The notion of feasible subspace dimension comes from [21]; we can add a visual explanation in the Appendix, as well as an explanation for eliciting the first two moments.  In line 287, there was a typo that muddled our intention: we meant ``a line in two-dimensional space’’, i.e. $\reals^2$.

We only speculate that a lower prediction dimension may imply lower sample complexity. Our intuition is that, all else equal, lower prediction dimension allows for an equally-expressive hypothesis class of smaller VC-dimension or Rademacher complexity, which implies a better sample complexity bound. It would be very interesting to formalize, but difficult because of the importance of the rest of the context (original prediction dimension, link function, hypothesis classes, …).  We will clarify this is speculation.
Thank you for other comments and suggestions.

\textbf{R6:}  It is a great point that we need to emphasize approximate minimizers while giving intuition for consistency, and we will clarify.  We will also direct the reader to Chapter 3 of [27] for intuition about the conditional problem.

Translating results from conditional distributions to those on $\X \times \Y$: this is rigorously addressed by [2] and [28], which we can emphasize. It would be interesting to explore conditions under which indirect elicitation is \emph{sufficient} for consistency. Since we assume $\Y$ is finite, we would only need to show indirect elicitation implies calibration, then cite prior work. This seems likely with reasonable restrictions on the link function.

Connection to the definition of calibration in [27]: you are correct. Calibration functions are especially important when considering generalization rates. In contrast, our interest in consistency precedes discussions of rates, which we hope to study in future work.

Technical difficulties with infinite infimum expected loss: We do avoid this problem in this paper by only considering situations where there always exists a minimizer of expected loss. For losses, this follows by definition of $\mathcal{L}$. For properties, it follows from nonemptiness. Understanding other cases is indeed interesting! We will emphasize this assumption throughout.

Thanks for the comments regarding definitions at the beginning of the paper. We feel that we seem to quickly require almost all these definitions to state results, except calibration. However, most ML readers wish to see how calibration relates, so we cannot drop it either.  We will carefully consider organization and these suggestions.

Thanks for all other comments.

>>>>

\usepackage{enumitem}

@@

\textbf{Examples:} We agree that earlier examples would be beneficial to help readers build intuition, and thank the reviewers for their suggestions. We will use abstain and variance as running examples starting from Section 2.

\textbf{Motivation to study prediction dimension:}  The computational (and perhaps sample) complexity of surrogate risk minimization is a function of the prediction dimension among other things.  A substantially lower prediction dimension, like the exponential reduction observed in the BEP abstain surrogate [22], can significantly improve the efficiency of the learning algorithm as a whole.  Understanding prediction dimension bounds is particularly important in structured prediction, but is also relevant in continuous estimation problems, one of our other ``quadrants’’.  Estimating risk and uncertainty are important problems in ML and statistics, and our results directly apply; see the applications to variance, entropy, distributional norms following Theorem 3.

\textbf{R1:}  We hope the earlier introduction of examples will improve clarity and improve the intuition for notation. $\ker(W)$ is the kernel of the matrix $W$. On broader impacts, we will expand on the potential negative impacts.

\textbf{R2:}  Thank you for the suggestion to add the implication interpretation of indirect elicitation.

@@

\textbf{R5:} Thank you for all your comments and suggestions.
\begin{itemize}[itemsep=1pt,topsep=0pt]
\item 
Regarding Theorems 2 and 3, it is correct that the best lower bound is the supremum over choices of $r$ and $p$. We agree that could be a good presentation, although stylistically we had reasons for our current approach. These include: this suprema does not seem to have a nice closed form; one’s intuition often leads to the best particular choice of $r$ and $p$; and this presentation matches that of [21, Theorem 16].

\item 
$\mathrm{relint}(\Delta_\Y)$ in Theorem 2: This assumption is actually WLOG, by restricting to a face (subsimplex) $F$ such that $p\in\mathrm{relint}(F)$. Corollary 1 applies Theorem 2 in this way to remove the $\mathrm{relint}(\Delta_\Y)$ assumption.

\item 
  While straightforward, we felt it important to emphasize Theorem 1 as it is not stated clearly in the literature, and indirect elicitation is not a well known tool to reason about consistency.

\item 
Citation on line 161: more general proofs have been derived by [28] (multiclass classification) and [21] (general matrix losses), but the proof is given most rigorously by [2]; we will add the other citations. We will also cite the NeurIPS 2012 version of [21].

\item 
The notion of feasible subspace dimension comes from [21]; we can add a visual explanation in the Appendix, as well as an explanation for eliciting the first two moments.  In line 287, there was a typo that muddled our intention: we meant ``a line in two-dimensional space’’, i.e. $\reals^2$.

\item 
We only speculate that a lower prediction dimension may help lower sample complexity. Our intuition comes from, e.g. sample complexity of learning a linear mapping from $\X$ to prediction space $\reals^n$ versus to $\reals^{\log n}$. It would be very interesting to formalize, but difficult because of the importance of the rest of the context (original prediction dimension, link function, hypothesis classes, …). We will clarify this is speculation.
\end{itemize}

\textbf{R6:} Thanks for all your comments.
\begin{itemize}[itemsep=1pt,topsep=0pt]
\item 
We will emphasize approximate minimizers while giving intuition for consistency; thank you for the suggestion.  We will also direct the reader to Chapter 3 of [27] for intuition about the conditional problem.

\item 
Translating results from conditional distributions to those on $\X \times \Y$ is rigorously addressed by [2] and [28], which we can emphasize. When indirect elicitation is \emph{sufficient} for consistency is an interesting question; one example is the class of polyhedral surrogates [5]. For finite $\Y$, one would only need to show indirect elicitation implies calibration, which seems likely to hold more generally with some restrictions on the link function.

\item 
Connection to the definition of calibration in [27]: you are correct. Calibration functions are especially important when considering generalization rates. In contrast, our interest in consistency precedes discussions of rates, which we hope to study in future work.

\item 
Infinite infimum expected loss: In this paper we assume there always exists a minimizer of expected loss. For losses, this follows by definition of $\mathcal{L}$. For properties, it follows from nonemptiness. Understanding other cases is indeed interesting; we will emphasize this assumption throughout.

\item 
Thanks for the comments regarding definitions at the beginning of the paper. We seem to quickly require almost all these definitions to state results, except calibration. We felt most ML readers will wish to see how calibration relates, however.  We will carefully consider organization and these suggestions.
\end{itemize}
